---
title: "EA-IRMS Processing Summary"
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
    self_contained: true
params:
  result: NULL
  config: NULL
  data_file: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

`%||%` <- function(x, y) {
  if (is.null(x)) y else x
}

result <- params$result
config <- params$config
data_file <- params$data_file
```

# Processing summary

This report documents the processing of the EA-IRMS dataset, including the
calibration diagnostics, correction decisions, and final processed output.

## Experiment information

```{r experiment-information}
experiment_info <- data.frame(
  Field = c(
    "Experiment",
    "File",
    "Peripheral",
    "Description"
  ),
  Value = c(
    config$experiment_name %||% NA_character_,
    config$file_name %||% NA_character_,
    "EA",
    config$description %||% NA_character_
  )
)

knitr::kable(experiment_info)
```

## Processing settings

```{r processing-settings}
processing <- config$processing %||% list()

processing_info <- data.frame(
  Setting = c(
    "Element",
    "Blank number",
    "Peak number"
  ),
  Value = c(
    processing$element %||% NA_character_,
    processing$blank_num %||% NA,
    processing$peak_number %||% NA
  )
)

knitr::kable(processing_info)
```

## Calibration standards

```{r calibration-standards}
calibration_standards <- NULL

if (!is.null(config$calibration_standards)) {
  calibration_standards <- config$calibration_standards
} else if (
  !is.null(config$standards) &&
  !is.null(config$standards$calibration_standards)
) {
  calibration_standards <- config$standards$calibration_standards
}

if (!is.null(calibration_standards) &&
    length(calibration_standards) > 0) {

  calibration_standards <- unlist(
    calibration_standards,
    use.names = TRUE
  )

  calibration_info <- data.frame(
    Element = names(calibration_standards),
    Calibration_standard = as.character(
      calibration_standards
    ),
    row.names = NULL
  )

  # Handle an unnamed single calibration standard gracefully.
  if (is.null(names(calibration_standards)) ||
      all(names(calibration_standards) == "")) {
    calibration_info$Element <- NA_character_
  }

  knitr::kable(calibration_info)

} else {

  cat("No calibration standards were recorded in the configuration.")
}
```

# Mass calibration

The mass calibration diagnostic was evaluated using the configured
calibration standard.

```{r mass-status, results='asis'}
if (isTRUE(result$apply_mass)) {
  cat("**Mass correction was applied.**")
} else if (identical(result$apply_mass, FALSE)) {
  cat("**Mass correction was not applied.**")
} else {
  cat("**Mass correction status was not recorded in the result object.**")
}
```

The diagnostic statistics and plot are shown regardless of whether the
correction was applied, so that the calibration decision can be reviewed.

```{r mass-statistics}
if (!is.null(result$mass_model)) {

  mass_summary <- data.frame(
    Metric = c(
      "Element",
      "Calibration standard",
      "Slope",
      "Intercept",
      "R-squared",
      "Residual standard error",
      "Number of measurements"
    ),
    Value = c(
      result$mass_model$element,
      result$mass_model$calibration_standard,
      result$mass_model$slope,
      result$mass_model$intercept,
      result$mass_model$r_squared,
      result$mass_model$residual_std_error,
      result$mass_model$n_measurements
    )
  )

  knitr::kable(mass_summary)
} else {
  cat("Mass calibration model was not available.")
}
```

## Mass calibration diagnostic

```{r mass-plot, fig.width=7, fig.height=5}
if (!is.null(result$mass_model) &&
    !is.null(result$mass_model$plot)) {

  print(result$mass_model$plot)

} else {

  cat("Mass calibration diagnostic plot was not available.")

}
```

# Blank correction

```{r blank-statistics}
if (!is.null(result$blank_stats)) {

  blank_summary <- data.frame(
    Metric = c(
      "Mean blank area",
      "SD blank area",
      "Mean blank delta",
      "SD blank delta",
      "Number of blanks"
    ),
    Value = c(
      result$blank_stats$mean_area,
      result$blank_stats$sd_area,
      result$blank_stats$mean_delta,
      result$blank_stats$sd_delta,
      result$blank_stats$n_blanks
    )
  )

  knitr::kable(blank_summary)

} else {

  cat("Blank statistics were not available.")

}
```

# Linearity calibration

The area-dependent linearity calibration diagnostic was evaluated using the
configured calibration standard.

```{r linearity-status, results='asis'}
if (isTRUE(result$apply_linearity)) {
  cat("**Linearity correction was applied.**")
} else if (identical(result$apply_linearity, FALSE)) {
  cat("**Linearity correction was not applied.**")
} else {
  cat("**Linearity correction status was not recorded in the result object.**")
}
```

The diagnostic statistics and plot are shown regardless of whether the
correction was applied, so that the calibration decision can be reviewed.

```{r linearity-statistics}
if (!is.null(result$linearity_model)) {

  linearity_summary <- data.frame(
    Metric = c(
      "Calibration standard",
      "Calibration reference",
      "Slope",
      "Intercept",
      "R-squared",
      "Residual standard error",
      "Number of standards",
      "Delta column"
    ),
    Value = c(
      result$linearity_model$calibration_standard,
      result$linearity_model$calibration_reference,
      result$linearity_model$slope,
      result$linearity_model$intercept,
      result$linearity_model$r_squared,
      result$linearity_model$residual_std_error,
      result$linearity_model$n_stds,
      result$linearity_model$delta_column
    )
  )

  knitr::kable(linearity_summary)

} else {

  cat("Linearity calibration model was not available.")

}
```

## Linearity calibration diagnostic

```{r linearity-plot, fig.width=7, fig.height=5}
if (!is.null(result$linearity_model) &&
    !is.null(result$linearity_model$plot)) {

  print(result$linearity_model$plot)

} else {

  cat("Linearity calibration diagnostic plot was not available.")

}
```

# Scale calibration

The scale calibration is the final calibration step and uses the standards
required by the scale model.

```{r scale-statistics}
if (!is.null(result$scale_model)) {

  scale_summary <- data.frame(
    Metric = c(
      "Slope",
      "Intercept",
      "R-squared",
      "Residual standard error",
      "Delta column",
      "Reference column",
      "Number of standards"
    ),
    Value = c(
      result$scale_model$slope,
      result$scale_model$intercept,
      result$scale_model$r_squared,
      result$scale_model$residual_std_error,
      result$scale_model$delta_column,
      result$scale_model$reference_column,
      result$scale_model$n_stds
    )
  )

  knitr::kable(scale_summary)

} else {

  cat("Scale calibration model was not available.")

}
```

# Final output

The processed output was generated by the EA processing pipeline.

```{r output-information}
if (!is.null(data_file)) {
  cat("Output data file: ", data_file)
}
```

## Processed data preview

```{r output-preview}
if (!is.null(result$output)) {

  knitr::kable(
    utils::head(result$output, 10)
  )

} else {

  cat("Final output data were not available in the result object.")

}
```
