---
title: "GC-IRMS Processing Summary"
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
    self_contained: true
params:
  result: NULL
  config: NULL
  data_file: NULL
  injection_offsets_file: NULL
  daily_offsets_file: NULL
  excluded_measurements_file: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
result <- params$result
config <- params$config
```

# Processing summary

This report summarizes GC peak assignment and date-specific external-standard
correction and, when configured, date-specific NACME derivatization correction.

## Experiment

```{r experiment}
methods <- unique(stats::na.omit(as.character(result$method_name)))
method_label <- if (length(methods) == 0) {
  NA_character_
} else {
  paste(methods, collapse = ", ")
}
info <- data.frame(
  Field = c("Experiment", "File", "Method", "Isotope", "External standard"),
  Value = c(
    config$experiment_name,
    config$file_name,
    method_label,
    result$isotope,
    result$external_standard_id
  )
)
knitr::kable(info)
```

## Compound assignments

```{r assignments}
assignment_summary <- result$data |>
  dplyr::count(compound_match_status, compound_id, name = "n_peaks")
knitr::kable(assignment_summary)
```

## External-standard offsets

Offsets are estimated per standard injection by averaging matched compound
offsets, then averaged without weighting across included injections by date.
Manual analysis exclusions are applied before these averages. Standard
injection IDs listed in the exclusion table below are omitted from offset
calculations. The daily offset is applied to non-standard peaks measured on
that date.

```{r injection-offsets}
knitr::kable(result$injection_offsets)
```

```{r daily-offsets}
knitr::kable(result$daily_offsets)
```

## Exclusions

Manual analysis or peak exclusions are listed here and are also saved to a
separate CSV file. An exclusion with a peak number removes that peak within
the selected analysis; an exclusion without one removes every peak from that
analysis. These rows are omitted before external-standard correction.

```{r manual-exclusions}
excluded_measurements <- result$excluded_measurements
if (is.null(excluded_measurements) || nrow(excluded_measurements) == 0) {
  cat("No manual measurement exclusions were applied.\n")
} else {
  knitr::kable(excluded_measurements)
}
```

The following external-standard injection IDs remain in the processed data
for review but do not contribute to injection or daily offset averages.

```{r standard-injection-exclusions}
excluded_standard_ids <- result$excluded_standard_injection_ids
if (is.null(excluded_standard_ids) || length(excluded_standard_ids) == 0) {
  cat("No external-standard injections were excluded from offset calculations.\n")
} else {
  knitr::kable(data.frame(
    excluded_standard_injection_id = excluded_standard_ids
  ))
}

missing_standard_ids <- result$missing_excluded_standard_injection_ids
if (!is.null(missing_standard_ids) && length(missing_standard_ids) > 0) {
  cat("Configured excluded standard IDs not found in this run: ",
      paste(missing_standard_ids, collapse = ", "), "\n", sep = "")
}

excluded_standard_compounds <- result$excluded_standard_compound_ids
if (is.null(excluded_standard_compounds) ||
    length(excluded_standard_compounds) == 0) {
  cat("No standard compounds were excluded from offset calculations.\n")
} else {
  cat("Standard compounds excluded from all offset averages:\n")
  knitr::kable(data.frame(
    excluded_standard_compound_id = excluded_standard_compounds
  ))
  cat("These compound measurements remain in the processed data.\n")
}

missing_standard_compounds <- result$missing_excluded_standard_compound_ids
if (!is.null(missing_standard_compounds) &&
    length(missing_standard_compounds) > 0) {
  cat("Configured excluded compound IDs not found in F8 measurements: ",
      paste(missing_standard_compounds, collapse = ", "), "\n", sep = "")
}

unmatched_manual_exclusions <- result$unmatched_measurement_exclusions
if (!is.null(unmatched_manual_exclusions) &&
    nrow(unmatched_manual_exclusions) > 0) {
  cat("Manual exclusion selectors that did not match any measurements:\n")
  knitr::kable(unmatched_manual_exclusions)
}
```

## Final corrected peak data

The CSV contains the raw and corrected isotope values, compound-assignment
status, retention time, peak area, and injection metadata.

```{r output-preview}
knitr::kable(utils::head(result$output, 20))
```
