---
title: "GC-IRMS Processing Summary"
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
    self_contained: true
params:
  result: NULL
  config: NULL
  data_file: NULL
  injection_offsets_file: NULL
  daily_offsets_file: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
result <- params$result
config <- params$config
```

# Processing summary

This report summarizes GC peak assignment and date-specific external-standard
correction. It does not apply derivatization or internal-standard corrections.

## Experiment

```{r experiment}
info <- data.frame(
  Field = c("Experiment", "File", "Method", "Isotope", "External standard"),
  Value = c(
    config$experiment_name,
    config$file_name,
    result$method_name,
    result$isotope,
    result$external_standard_id
  )
)
knitr::kable(info)
```

## Compound assignments

```{r assignments}
assignment_summary <- result$data |>
  dplyr::count(compound_match_status, compound_id, name = "n_peaks")
knitr::kable(assignment_summary)
```

## External-standard offsets

Offsets are estimated per standard injection by averaging matched compound
offsets, then averaged across injections by date. The daily offset is applied
to non-standard peaks measured on that date.

```{r injection-offsets}
knitr::kable(result$injection_offsets)
```

```{r daily-offsets}
knitr::kable(result$daily_offsets)
```

## Final corrected peak data

The CSV contains the raw and corrected isotope values, compound-assignment
status, retention time, peak area, and injection metadata.

```{r output-preview}
knitr::kable(utils::head(result$output, 20))
```
