---
title: "EA-IRMS Correction Report"
author:
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
---

# Purpose

This report runs the EA-IRMS processing pipeline documents the resulting corrections. Replace file paths in set-up, and check parameters for the corrections are as intended.

The pipeline produces two final files:

1. A corrected CSV containing the final analysis-ready data.
2. This HTML report containing the processing steps, calibration statistics, diagnostic plots, and final checks.

# 1. Setup

```{r load config}
data_path <- file.path(
  "path",
  "to",
  "data",
  "directory"
)

config_path <- file.path(
  data_path,
  "analyzed_data",
  "experiment_config.yaml"
)

config <- load_IRMS_config(config_path)

raw_data_path <- file.path(
  "..",
  config$raw_data_dir,
  paste0(config$file_name, ".xls")
)

raw_ea <- readxl::read_xls(raw_data_path)

schema_path <- file.path(
  "inst",
  "config",
  "peripheral_schemas.yml"
)

schemas <- load_peripheral_schemas(schema_path)

schema <- get_peripheral_schema(
  schemas = schemas,
  peripheral = "EA"
)

stds_reference_df <- config$stds_reference_df

output_path <- file.path(
  data_path,
  "analyzed_data"
)

```

# 2. Run corrections

```{r test result}

result <- process_ea(
  raw_df = raw_ea,
  config = config,
  schema = schema,
  stds_reference_df = stds_reference_df,
  isotope = "C13",
  run_id = config$file_name,
  instrument = "EA",
  apply_mass = TRUE,
  apply_linearity = TRUE,
  verbose = TRUE
)

```

# 3. Save results

```{r save result}

saved <- save_ea_results(
  result = result,
  config = config,
  output_dir = output_path
)

```
